Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-12 WSSSPE3/report/wg_main_best_practices.tex
fixing WSSSPE spelling

\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSPEx\cite{WSSPE papers, heroux paper, ...} and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g. a journal paper, tutorial etc.)  that can be widely disseminated is necessary and likely to be very valuable.

@@

The creation of such a ``best practices" document will build upon the range of activities and topics discussed at WSSPE3 and associated prior meeting. We will attempt to
distill the emerging body of knowledge into this document. The large number of  articles from the NSF funded S2I2 projects (SSE and SSI) ``lightning talks", ``white papers"  and reports from different workshops point have created a large if somewhat diffuse source for this report.

@@

\subsubsection{Plans}
%\todo{short text here - not bullets}
The creation of a best-practices document needs a large and diverse community involved. We have enlisted over ten contributors from the attendees at the WSSPE3 and 
those on the mailing list. The primary mechanism for developing these will be to examine and analyze the success of several well known community scientific
software and organizations supporting scientific software. We will attempt then to abstract general principles and best practices. Some of the tools identified for such analysis are
the general purpose PeTSC toolkit for linear system solution, NWChem for computational chemistry and the CIG (Computational Infrastructure for Geodynamics) organization dedicated to supporting an ensemble of related tools for the geodynamics community. 
We also established a timeline and a rough outline for the report.

>>>>

\subsubsection{Why it is important}
Reviewing multiple past articles and talks at different meetings like WSSSPEx\cite{WSSSPE papers, heroux paper, ...} and 
analyzing and promoting sustainable scientific software makes it clear that there 
are several common and recurring ideas that underpin success. However, outside of a small community, this knowledge is not widely
shared. This is  especially true for the large community of scientists who generate most of the software used by scientists but are not primarily software developers. In this
scenario a clear and precise exposition of these best practices collected from many sources and open collaboration among all in the community
in a single source (e.g. a journal paper, tutorial etc.)  that can be widely disseminated is necessary and likely to be very valuable.

@@

The creation of such a ``best practices" document will build upon the range of activities and topics discussed at WSSSPE3 and associated prior meeting. We will attempt to
distill the emerging body of knowledge into this document. The large number of  articles from the NSF funded S2I2 projects (SSE and SSI) ``lightning talks", ``white papers"  and reports from different workshops point have created a large if somewhat diffuse source for this report.

@@

\subsubsection{Plans}
%\todo{short text here - not bullets}
The creation of a best-practices document needs a large and diverse community involved. We have enlisted over ten contributors from the attendees at the WSSSPE3 and 
those on the mailing list. The primary mechanism for developing these will be to examine and analyze the success of several well known community scientific
software and organizations supporting scientific software. We will attempt then to abstract general principles and best practices. Some of the tools identified for such analysis are
the general purpose PeTSC toolkit for linear system solution, NWChem for computational chemistry and the CIG (Computational Infrastructure for Geodynamics) organization dedicated to supporting an ensemble of related tools for the geodynamics community. 
We also established a timeline and a rough outline for the report.
